Yeast RNA-seq 48 sample simulation study

### 2018-05-31 datasets/RNA-Seq/yeast-simulation.Rmd
Add status label to qqplot diagnostics

# qqplots
plotfile <- file.path(datdir, "null10_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

# qqplots
plotfile <- file.path(datdir, "de5_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

# qqplots
plotfile <- file.path(datdir, "de10_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

>>>>

# qqplots
plotfile <- file.path(datdir, "null10_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null10, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

# qqplots
plotfile <- file.path(datdir, "de5_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(de5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

# qqplots
plotfile <- file.path(datdir, "de10_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(de10, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```
